Reproducibility of published meta-analyses on clinical psychological

### 2023-06-21 revision/response_letter2.Rmd

---
title       : "Reproducibility of published meta-analyses on clinical psychological
  interventions"
authors     : "Ruben Lopez-Nicolas et al."
journal     : "Advances in Methods and Practices in Psychological Science"
manuscript  : "AMPPS-22-0119"

class       : "draft"
output      : papaja::revision_letter_pdf
---

Dear Dr. Flake,

Thank you again for taking your time reviewing and handling our manuscript. Next, we provide point by point answers to your comments and specify how we have addressed them in the revised manuscript.

# Comments

\RC {The Abstract:

Thank you for clarifying the results in the abstract. I think it is an improvement, but I'm concerned the take-aways are unclear and would clarify a few points in the abstract.

 -Your revised text says that 10 discrepancies were resolved  "after fixing a coding error" -- made by who, the authors of the meta-analysis or are these ones where you found your own error?}

Here, we are referring to coding errors made by ourselves when we retrieved data from document formats. We agree that it could be a bit confusing. We have added the following clarification (see Abstract):

>For 10 meta-analyses this discrepancy was solved after fixing a coding error \textcolor{blue}{of our data retrieval process}...

\RC{-A summary sentence that clarifies the major takeaway in connection to data availability and then reproduction would be helpful. From my reading of the results it seems that at the end, there were 27 that were never resolved, meaning that the biggest threat to reproduction is data can't be located, once you can get the data the majority of studies can be reproduced (though not perfectly, which is important).}

We have added a few additional sentences in the abstract related to data availability to highlight this issue, mention changes over time, and point out the type of data availability (see Abstract):

>The original data were retrieved for 67% (146/217) meta-analyses. \textcolor{blue}{While this rate showed an improvement over the years, in only 5\% of these cases was it possible to retrieve a data file ready for reuse.} Of these 146, 52 showed a discrepancy larger than 5% in the main results in the first stage. For 10 meta-analyses this discrepancy was solved after fixing a coding error \textcolor{blue}{of our data retrieval process} and for 15 of them it was considered approximately reproduced in a qualitative assessment. In the remaining meta-analyses (18%, 27/146), different issues were identified in an in-depth review, such as reporting inconsistencies, lack of data, or transcription errors. Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions. \textcolor{blue}{Overall, one of the biggest threats to the reproducibility of meta-analysis is related to data availability and current data sharing practices in meta-analysis.}

\RC{Main text:

-The last sentence on page 7 isn't clear, reproducing primary effect sizes versus the ones already coded by the original authors – the distinction is more clear on page 9, but please revise this sentence to be very direct as to what you are referring to a bit earlier in the paper.}

Indeed, this sentence isn’t accurate. We have rephrased it (see p. 7):

>...Where previous work focused on the reproducibility of primary effect sizes \textcolor{blue}{by recoding data from primary studies}, we explored meta-analysis outcome reproducibility using the primary \textcolor{blue}{data} already coded by the original authors. \textcolor{blue}{Therefore, we attempted to retrieve the data shared by the authors of the meta-analysis.}

\RC{-Even on page 9, I still think a bit more could be clarified on page 9 to make very obvious what was in the primary original study, in the meta-analysis done by the meta analytic authors, and then what you sought to do.}

In the same vein, we have added a clarification in this section (see p. 9):

>In order to be able to reproduce meta-analyses of aggregate data, primary-level^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data \textcolor{blue}{shared by the authors of the meta-analysis...}

\RC{Main Text, Supplement, and discussion:

 I didn't find the logistic regression without any descriptive information in the supplement to be very helpful. I would like to see more descriptive information in the main text and the supplement and for the discussion to be updated accordingly.

 -In the main manuscript I think it would be best to provide some descriptive information about the publication year of the MA and data retrieval. Given you mention this in the discussion, having some results in the main paper is helpful, but I do not think a full statistical analysis is needed.  The year and data availability would be more useful with descriptive statistics – I'm thinking a crosstabs or a graph that shows the rate of availability by year and the sample size. We cannot make strong inferences here given the limited data, but you can cautiously note a trend.}

Following your recommendation, we have complemented Figure 3a by adding three new bars displaying rates for different time periods (see Figure 3, p. 16).

Additionally, we have mentioned that in the results section (see p. 13 and 14):

>Figure 3 summarizes the primary data retrieval results. Based on the availability of primary data, either retrieved directly from the paper or upon request, 146 meta-analyses 146 meta-analyses (67%, see Fig. 3a) were labelled as process reproducible. \textcolor{blue}{Additionally, as the time span covered is fairly wide, the process reproducible rate was also computed for different time periods. The meta-analyses were grouped into five-year periods, except for the initial period, which was grouped into a ten-year period due to the limited number of meta-analyses available during the first five-year period, which consisted of only five meta-analyses. The process reproducibility rate was 41\%, (12/29), 59\%, (44/75), and 80\%, (90/113) for meta-analyses published between 2000 and 2010, 2011 and 2015, and 2016 and 2020, respectively (see Fig. 3a). This trend is further explored in the Supplementary file available at: https://osf.io/fjhpw.}

Furthermore, we have slightly modified the discussion by mentioning the new results reported in the main text (see p. 22):

>Nevertheless, a more positive sign comes from the positive association between publication year and the possibility of retrieving the data. \textcolor{blue}{The results tentatively suggest a trend of improving data availability over the years, with a notable rate of 80\% observed in meta-analyses published between 2016 and 2020...}

\RC{-You can keep the logistic regression if you'd like, but without sample size info by year and basic descriptive statistics, it isn't very interpretable, so this needs included with some detail in the supplement as well. Converting the coefficients into odds and then percentages would also help.}

We have also added more information in this regard in the supplementary file (see p. 4 in Supplementary file):

>\textcolor{blue}{The publication year range of the included meta-analyses in our study is quite extensive. The initial pool, from which we randomly selected a sample, comprised meta-analytic reports published between 2000 and 2020, encompassing a span of two decades. For our analysis, we focused on a random sample of 100 of these meta-analytic reports.  From the 100 included reports, 217 independent meta-analyses were selected following the criteria explained in the ‘Identification and selection of articles and meta-analyses’ section of the main paper. These meta-analyses were published between 2001 and 2020 (mean = 2015.04; sd = 4.05; median =
2016; interquartile range = 2012-2016). As an unrestricted random sample, the publication year distribution is clearly left-skewed, with 92.2\% of the included meta-analyses published between 2010 and 2020 (see Figure 2 of the main paper for the full distribution).}

>\textcolor{blue}{As shown in the main paper (see Figure 3a), there appears to be an improvement in the rate of data availability over the years. The overall data availability rate for the full sample was found to be 67\%. However, when examining meta-analyses published within specific time periods, the rates varied. For meta-analyses published between 2000 and 2010, the data availability rate was 41\%. For those published between 2011 and 2015, the rate increased to 59\%. Notably, meta-analyses published between 2016 and 2020 exhibited the highest data availability rate of 80\%. These findings suggest a positive trend of improved data availability in more recent years.}

Moreover, a new column reporting the percentage change associated with the ORs has been added to Table 2 of the Supplementary file:

>Based on the results of the four models, there seems to be an association between the publication year and the possibility of retrieving primary data from a meta-analysis. We found that all 4 ORs computed were > 1, indicating a higher probability of retrieving data the more recent the publication year of the meta-analysis. \textcolor{blue}{Specifically, the odds increased from 11.85\% to 34.46\% per year...}

### 2023-06-21 submission.Rmd
Second revision

abstract: |
  Meta-analysis is one of the most useful research approaches, the relevance of which relies on its credibility. However, in recent years different concerns about the credibility of psychological research have emerged. Reproducibility of scientific results could be considered as the minimal threshold of it. Our purpose was to assess the reproducibility of a sample of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files, or requesting it from original authors. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses. Of these, 52 showed a discrepancy larger than 5% in the main results in the first stage. \textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors. \textcolor{blue}{Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

@@

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020]. Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009], possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage. \textcolor{blue}{In this project we focus on the last stage, related to the statistical analysis and quantitative results of the synthesis.}

@@

Reproducibility analysis \textcolor{blue}{of reported quantitative results} typically uses the original data available from the original authors [e.g., @artner2020; @hardwicke2021; @hardwicke2018]. This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc. Although data availability seems to have improved in the last years [@hardwicke2018; @tedersoo2021; @wallach2018], systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies which is commonly reported in the paper through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For example, @page2022 analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is not applicable as no datasets were generated, 8% stating that data sharing is not applicable as the data is drawn from already published literature, and 42% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis  assume that such practices do not apply to meta-analyses, or that the data in the article itself is sufficient.

## Purpose 
Previous research has revealed that there is room for improvement at different stages of the meta-analytic process pipeline. In this study our purpose is twofold. First, we broadened previous process reproducibility assessments by considering data availability on request and by contacting original authors to request required information to reproduce the meta-analysis. Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data. Where previous work focused on the reproducibility of primary effect sizes, we explored meta-analysis outcome reproducibility using the primary effects sizes already coded by the original authors.

@@

\textcolor{blue}{Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.}

# Method
## Identification and selection of articles and meta-analyses 
In previous research we identified a pool of 664 meta-analytic reports on clinical psychological interventions published between 2000 and 2020 through a systematic electronic search [@lopez-nicolas2021]. Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the random selection process is available at: https://osf.io/cp293/. \textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for `r n_mas_less_10` of the articles included in this report. \textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}

@@

## Retrieval of primary data
In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows: 
$$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$
with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $(1 - {\alpha/2})\%$ percentile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a two-sided 95% confidence interval).

\textcolor{blue}{On the other hand, efforts were also made to retrieve the most reusable data possible.} First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. Finally, if the primary data of a meta-analysis were not directly available after the previous steps, we attempted to obtain the data through a request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and, if there was no reply, a subsequent reminder in October 2021. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.

## Reconstructing the original analytical scheme
To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, reproducibility was checked by rerunning the original script on the associated primary data. When it was not available, we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis. If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*. \textcolor{blue}{We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.}

@@

## Data collection procedure 
\textcolor{blue}{Data collection procedure was carried out by five of the authors.} At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus. Next, the initial pool of 100 included articles was split among four coders, 25 articles each. A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding, with the goal to examine the reliability of the data collection process. Disagreements were resolved by consensus and by double-checking the original materials. \textcolor{blue}{Details about inter-coder agreement are reported in the Supplementary file.}

## Reproducibility outcomes
Each meta-analysis was labelled using the following \textcolor{blue}{two-level}^[This hierarchy is a minor deviation from the pre-registered protocol. It is essentially the same and the results are identical. It was introduced to improve clarity.] reproducibility success scheme. \textcolor{blue}{First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible. In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request}^[Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt. In our study, this is equivalent to data availability due to our design and the stage of the meta-analysis pipeline we focused on.]. \textcolor{blue}{Second, those labelled as process-reproducible} were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.  Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/). This index expressed the difference between reproduced and original values as a percentage. To avoid labelling minor numerical discrepancies related to numerical rounding as reproducibility problems, a 5% discrepancy threshold was set. Thus, a meta-analysis was labelled as 'numerical error' if it showed a discrepancy larger than 5%.^[A sensitivity analysis using other possible criteria is reported in the supplementary file.] 
Finally, the label 'decision error' refers to situations where the $p_{reported}$ fell on the opposite side of the .05 boundary in relation to the $p_{reproduced}$.

@@

\textcolor{blue}{Finally, the association between publication year and the possibility of retrieving the data in one of the ways conducted in this project were explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable. We quantified the strength of the association by calculating odds ratios and 95\% confidence intervals based on the profile likelihood. These exploratory analyses were  not pre-registered. Details and results are reported in Supplementary file.}

@@

From the 100 included papers, `r n_mas_total` independent meta-analyses were selected following the criteria explained above. These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`), \textcolor{blue}{and were cited `r round(cc_mean, 2)` times on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", cc_sd, cc_median, cc_q1, cc_q3, cc_range[1], cc_range[2])`}^[Citation counts were retrieved from CrossRef API using the *rcrossref* package [@rcrossref]. For two cases in which CrossRef did not return data, citation counts were consulted in Google Scholar. Both queries were done on 20/03/2023.]. 
Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample \textcolor{blue}{(panel A), the publication year distribution among the papers included in our sample (panel B) as well as the citation count distribution of those papers (panel C).} Original results and characteristics of these meta-analyses are available at: https://osf.io/8jzbk

@@

## Process reproducibility 
Figure 3 summarizes the primary data retrieval results. Based on the availability of primary data, either retrieved directly from the paper or upon request, `r df_process_rep$n[2]` meta-analyses (`r sprintf("%0.0f%%", df_process_rep$perc[2]*100)`, see Fig. 3a) were labelled as process reproducible. Of these `r df_process_rep$n[2]` meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files (see Fig. 3b for further details). 
Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers by emailing the corresponding authors, data was only retrieved for `r df_source_primary_data$n[1]` meta-analyses, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%, %0.0f/%0.0f", df_request$perc[2]*100, df_request$n[2], sum(df_request$n))`, see Fig. 3c). For the remaining `r df_process_rep$n[1]` from `r df_request$n[1] + df_request$n[3]` different papers, a reply providing some reasons not to share was received in `r sprintf("%0.0f%% (%0.0f/%0.0f,  see Fig 3c)", df_request$perc[3]*100, df_request$n[3], sum(df_request$n))`, whereas no reply was received for the remainder of the meta-analyses. Table 1 summarises the different reasons corresponding authors given when data was not provided upon request.

@@

## Funding 
This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00/AEI/10.13039/501100011033, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).

>>>>

abstract: |
  Meta-analysis is one of the most useful research approaches, the relevance of which relies on its credibility. Reproducibility of scientific results could be considered as the minimal threshold of this credibility. We assessed the reproducibility of a sample of meta-analyses published between 2000-2020. From a random sample of 100 papers reporting results of meta-analyses of interventions in clinical psychology, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files, or requesting it from original authors. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis. The original data were retrieved for 67% (146/217) meta-analyses. \textcolor{blue}{While this rate showed an improvement over the years, in only 5\% of these cases was it possible to retrieve a data file ready for reuse.} Of these 146, 52 showed a discrepancy larger than 5% in the main results in the first stage. For 10 meta-analyses this discrepancy was solved after fixing a coding error \textcolor{blue}{of our data retrieval process} and for 15 of them it was considered approximately reproduced in a qualitative assessment. In the remaining meta-analyses (18%, 27/146), different issues were identified in an in-depth review, such as reporting inconsistencies, lack of data, or transcription errors. Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions. \textcolor{blue}{Overall, one of the biggest threats to the reproducibility of meta-analysis is related to data availability and current data sharing practices in meta-analysis.}

@@

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020]. Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009], possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage. In this project we focus on the last stage, related to the statistical analysis and quantitative results of the synthesis.

@@

Reproducibility analysis of reported quantitative results typically uses the original data available from the original authors [e.g., @artner2020; @hardwicke2021; @hardwicke2018]. This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc. Although data availability seems to have improved in the last years [@hardwicke2018; @tedersoo2021; @wallach2018], systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies which is commonly reported in the paper through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For example, @page2022 analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is not applicable as no datasets were generated, 8% stating that data sharing is not applicable as the data is drawn from already published literature, and 42% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis  assume that such practices do not apply to meta-analyses, or that the data in the article itself is sufficient.

## Purpose 
Previous research has revealed that there is room for improvement at different stages of the meta-analytic process pipeline. In this study our purpose is twofold. First, we broadened previous process reproducibility assessments by considering data availability on request and by contacting original authors to request required information to reproduce the meta-analysis. Second, we verified the outcome reproducibility of the meta-analyses that were process-reproducible using the available data. Where previous work focused on the reproducibility of primary effect sizes \textcolor{blue}{by recoding data from primary studies}, we explored meta-analysis outcome reproducibility using the primary \textcolor{blue}{data} already coded by the original authors. \textcolor{blue}{Therefore, we attempted to retrieve the data shared by the authors of the meta-analysis.}

@@

Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.

# Method
## Identification and selection of articles and meta-analyses 
In previous research we identified a pool of 664 meta-analytic reports on clinical psychological interventions published between 2000 and 2020 through a systematic electronic search [@lopez-nicolas2021]. Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the random selection process is available at: https://osf.io/cp293/. This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.
From these 100 articles, each independent pairwise meta-analytic model of aggregate data fitted on at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for `r n_mas_less_10` of the articles included in this report. This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.

@@

## Retrieval of primary data
In order to be able to reproduce meta-analyses of aggregate data, primary-level^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data \textcolor{blue}{shared by the authors of the meta-analysis.} First, we sought for the statistics used to compute primary effect sizes (e.g., means, sd); second, we sought for the primary effects sizes already computed and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows: 
$$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$
with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $(1 - {\alpha/2})\%$ percentile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a two-sided 95% confidence interval).

On the other hand, efforts were also made to retrieve the most reusable data possible. First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. Finally, if the primary data of a meta-analysis were not directly available after the previous steps, we attempted to obtain the data through a request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and, if there was no reply, a subsequent reminder in October 2021. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.

## Reconstructing the original analytical scheme
To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, reproducibility was checked by rerunning the original script on the associated primary data. When it was not available, we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis. If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*. We designed this procedure to reconstruct the original analytical scheme when the original analysis script was not available instead of trying to request it from the original authors due to: (a) not necessarily all authors of included meta-analyses will actually have an analysis script to share, because many might have used point and click software, and (b) we expected analysis script availability to be very low, and requesting it would have meant sending request for virtually every paper included in our re-analysis.

@@

## Data collection procedure 
Data collection procedure was carried out by five of the authors. At a first pilot stage, a random sample of five articles of the total pool was independently coded by the five members and, subsequently, in a series of meetings, disagreements between the coders were resolved by consensus. Next, the initial pool of 100 included articles was split among four coders, 25 articles each. A random sample of 25 articles of the total pool was assigned to the fifth member to carry out independent double-coding, with the goal to examine the reliability of the data collection process. Disagreements were resolved by consensus and by double-checking the original materials. Details about inter-coder agreement are reported in the Supplementary file.

## Reproducibility outcomes
Each meta-analysis was labelled using the following two-level^[This hierarchy is a minor deviation from the pre-registered protocol. It is essentially the same and the results are identical. It was introduced to improve clarity.] reproducibility success scheme. First, each meta-analysis was labelled as: (a) process-reproducible; and (b) not process-reproducible. In our study, not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request^[Process reproducibility, as described above, could imply a different situation if more conditions need to be met to proceed with the reproduction attempt. In our study, this is equivalent to data availability due to our design and the stage of the meta-analysis pipeline we focused on.]. Second, those labelled as process-reproducible were labelled as: (a) reproducible; (b) numerical error; and (c) decision error.  Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/). This index expressed the difference between reproduced and original values as a percentage. To avoid labelling minor numerical discrepancies related to numerical rounding as reproducibility problems, a 5% discrepancy threshold was set. Thus, a meta-analysis was labelled as 'numerical error' if it showed a discrepancy larger than 5%.^[A sensitivity analysis using other possible criteria is reported in the supplementary file.] 
Finally, the label 'decision error' refers to situations where the $p_{reported}$ fell on the opposite side of the .05 boundary in relation to the $p_{reproduced}$.

@@

Finally, the association between publication year and the possibility of retrieving the data in one of the ways conducted in this project were explored by fitting binary logistic regression models with publication year as predictor and process-reproducibility as dependent variable. We quantified the strength of the association by calculating odds ratios and 95\% confidence intervals based on the profile likelihood. These exploratory analyses were  not pre-registered. Details and results are reported in Supplementary file.

@@

From the 100 included papers, `r n_mas_total` independent meta-analyses were selected following the criteria explained above. These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`, and were cited `r round(cc_mean, 2)` times on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", cc_sd, cc_median, cc_q1, cc_q3, cc_range[1], cc_range[2])`^[Citation counts were retrieved from CrossRef API using the *rcrossref* package [@rcrossref]. For two cases in which CrossRef did not return data, citation counts were consulted in Google Scholar. Both queries were done on 20/03/2023.]. 
Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample (panel A), the publication year distribution among the papers included in our sample (panel B) as well as the citation count distribution of those papers (panel C). Original results and characteristics of these meta-analyses are available at: https://osf.io/8jzbk

@@

## Process reproducibility 
Figure 3 summarizes the primary data retrieval results. Based on the availability of primary data, either retrieved directly from the paper or upon request, `r df_process_rep$n[2]` meta-analyses (`r sprintf("%0.0f%%", df_process_rep$perc[2]*100)`, see Fig. 3a) were labelled as process reproducible. \textcolor{blue}{Additionally, as the time span covered is fairly wide, the process reproducible rate was also computed for different time periods. The meta-analyses were grouped into five-year periods, except for the initial period, which was grouped into a ten-year period due to the limited number of meta-analyses available during the first five-year period, which consisted of only five meta-analyses. The process reproducibility rate was }`r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep2$perc[2]*100, df_process_rep2$n[2], sum(df_process_rep2$n))`, `r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep3$perc[2]*100, df_process_rep3$n[2], sum(df_process_rep3$n))`, and `r sprintf("%0.0f%%, (%0.0f/%0.0f)", df_process_rep4$perc[2]*100, df_process_rep4$n[2], sum(df_process_rep4$n))` \textcolor{blue}{for meta-analyses published between 2000 and 2010, 2011 and 2015, and 2016 and 2020, respectively (see Fig. 3a). This trend is further explored in the Supplementary file available at: https://osf.io/fjhpw.}

Of these `r df_process_rep$n[2]` meta-analyses, in about half of the cases the primary data was retrieved from a forest plot in the paper itself and in about a third of the cases the primary data was retrieved from supplementary files (see Fig. 3b for further details). 
Although attempts were made to retrieve data for `r df_process_rep$n[1]+df_source_primary_data$n[1]` meta-analyses from `r sum(df_request$n)` different papers by emailing the corresponding authors, data was only retrieved for `r df_source_primary_data$n[1]` meta-analyses, from `r df_request$n[2]` different papers (`r sprintf("%0.0f%%, %0.0f/%0.0f", df_request$perc[2]*100, df_request$n[2], sum(df_request$n))`, see Fig. 3c). For the remaining `r df_process_rep$n[1]` from `r df_request$n[1] + df_request$n[3]` different papers, a reply providing some reasons not to share was received in `r sprintf("%0.0f%% (%0.0f/%0.0f,  see Fig 3c)", df_request$perc[3]*100, df_request$n[3], sum(df_request$n))`, whereas no reply was received for the remainder of the meta-analyses. Table 1 summarises the different reasons corresponding authors given when data was not provided upon request.

@@

## Funding 
This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00/AEI/10.13039/501100011033, and PID2019-104033GA-I00/MCIN/AEI/10.13039/501100011033, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).
